---
title: "Analysis_sockult"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
library(tidyverse)
```

#-----DATA CLEANING------

#Importing dataframe and extracting all participants who finished as well as offer and response columns
```{r warning=FALSE, include=FALSE}

wide<-read.csv("data/all_apps_wide_2021-05-10.csv") #loading the wide dataframe with all data from oTree

df_wide<-filter(wide, wide$participant._current_page_name == "ThankYou")#filtering all participants who did not finish the experiment away. The last page in the experiment is called "ThankYou".
wide$participant.code<-as.factor(wide$participant.code)
df_wide<-df_wide[-c(1), ] 

Columns_offers<-grep(pattern="\\.Offer$", #Filtering the df_wide dataframe for all columns where participants give offers
    x=colnames(df_wide))

Columns_responds<-grep(pattern="\\.bot_side$", #Filtering the df_wide dataframe for all columns where bot responds
    x=colnames(df_wide))

Columns_description<-grep(pattern="\\.about_you$", #Filtering the df_wide dataframe for all columns where bot responds
    x=colnames(df_wide))

Persona_player<-grep(pattern="\\.P$", #Filtering the df_wide dataframe for all columns where bot responds
    x=colnames(df_wide))

OfferDf<- df_wide[, colnames(df_wide)[Columns_offers]] #A df with data from offers

ResponseDf<-df_wide[, colnames(df_wide)[Columns_responds]]  #A df with bot response

about_youDf<-df_wide[, colnames(df_wide)[Columns_description]]  #A df with the participants descriptions

```


-
#offer df
```{r include=FALSE}
#Extracting participant code, age and gender and adding them to the OfferDf
OfferDf["ParticipantCode"] <- df_wide$participant.code 
OfferDf["Age"] <- df_wide$Consentform.1.player.Age
OfferDf["Gender"] <- df_wide$Consentform.1.player.Gender

#relocating to the beginning of the dataframe
OfferDf <- OfferDf %>% 
  relocate(ParticipantCode, Age, Gender, .before =ultimatumn_anonym.1.player.Offer)

#renaming columns 
colnames(OfferDf) <- sub(".player.Offer", "", colnames(OfferDf))
colnames(OfferDf) <- sub("Persona", "P", colnames(OfferDf))
colnames(OfferDf) <- sub("ultimatumn_anonym", "An", colnames(OfferDf))
colnames(OfferDf) <- sub("An.1", "An1", colnames(OfferDf))
colnames(OfferDf) <- sub("An.2", "An1.2", colnames(OfferDf))
colnames(OfferDf) <- sub("An.3", "An1.3", colnames(OfferDf))
colnames(OfferDf) <- sub("An.4", "An1.4", colnames(OfferDf))
colnames(OfferDf) <- sub("An.5", "An1.5", colnames(OfferDf))
colnames(OfferDf) <- sub("An.6", "An1.6", colnames(OfferDf))
colnames(OfferDf) <- sub("An.7", "An1.7", colnames(OfferDf))
colnames(OfferDf) <- sub("An.8", "An1.8", colnames(OfferDf))
colnames(OfferDf) <- sub("An.9", "An1.9", colnames(OfferDf))
colnames(OfferDf) <- sub("An.10", "An10", colnames(OfferDf))
```


-
#response df
```{r include=FALSE}
#Doing the same
ResponseDf["ParticipantCode"] <- df_wide$participant.code 
ResponseDf["Age"] <- df_wide$Consentform.1.player.Age
ResponseDf["Gender"] <- df_wide$Consentform.1.player.Gender

colnames(ResponseDf) <- sub("ultimatumn_anonym", "An", colnames(ResponseDf))
colnames(ResponseDf) <- sub("player.bot_side", "Response", colnames(ResponseDf))
colnames(ResponseDf) <- sub("ultimatumn_anonym", "An", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.1", "An1", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.2", "An1.2", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.3", "An1.3", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.4", "An1.4", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.5", "An1.5", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.6", "An1.6", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.7", "An1.7", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.8", "An1.8", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.9", "An1.9", colnames(ResponseDf))
colnames(ResponseDf) <- sub("An.10", "An10", colnames(ResponseDf))
colnames(ResponseDf) <- sub("Persona", "P", colnames(ResponseDf))

ResponseDf <- ResponseDf %>% 
  relocate(ParticipantCode, Age, Gender, .before =An1.Response)
```

-
#Creating dataframe with responses and offers 
```{r include = FALSE}
#Combining responsedf and offerdf
Combined<-cbind(ResponseDf, OfferDf)

#including participants

Combined["ParticipantCode"] <- df_wide$participant.code 
Combined["Age"] <- df_wide$Consentform.1.player.Age
Combined["Gender"] <- df_wide$Consentform.1.player.Gende

#removing 
colnames(Combined ) <- sub(".player.Offer", "", colnames(Combined ))
colnames(Combined ) <- sub("Persona", "P", colnames(Combined ))
colnames(Combined) <- sub("player.bot_side", "Response", colnames(Combined))
colnames(Combined ) <- sub("ultimatumn_anonym", "An", colnames(Combined ))
colnames(Combined ) <- sub("An.1", "An1", colnames(Combined ))
colnames(Combined ) <- sub("An.2", "An1.2", colnames(Combined ))
colnames(Combined ) <- sub("An.3", "An1.3", colnames(Combined ))
colnames(Combined ) <- sub("An.4", "An1.4", colnames(Combined ))
colnames(Combined ) <- sub("An.5", "An1.5", colnames(Combined ))
colnames(Combined ) <- sub("An.6", "An1.6", colnames(Combined ))
colnames(Combined ) <- sub("An.7", "An1.7", colnames(Combined ))
colnames(Combined ) <- sub("An.8", "An1.8", colnames(Combined ))
colnames(Combined ) <- sub("An.9", "An1.9", colnames(Combined ))
colnames(Combined ) <- sub("An.10", "An10", colnames(Combined ))

Combined <- Combined %>% 
  relocate(Gender, .before =An1.Response)

```


-
#From wide to long format
```{r warning=FALSE, include=FALSE}
#from wide to long format for the Offer only df
df_long<-reshape(OfferDf, 
        direction = "long",
        varying = list(names(OfferDf)[4:83]),
        v.names = "Offer",
        idvar = c("ParticipantCode", "Age", "Gender"),
        timevar = "Round",
        times = c(names(OfferDf)[4:83]))

#Using a combined dataframe to convert response to long format
df_respons_long<-reshape(Combined, 
        direction = "long",
        varying = list(names(Combined)[4:83]),
        v.names = "Response",
        idvar =  "ParticipantCode",
        timevar = "Round",
        times = c(names(Combined)[4:83]))
```


-
#Creating Is_anonymous, OtherPlayer, PrevOffer, PrevResonse, centered_PrevOffer
```{r warning=FALSE}

df_long["Response"]<- df_respons_long$Response
df_long["Is_anonymous"] <- ifelse(grepl("An",df_long$Round),'1','0')

x<-rep(c(1,2,3,4,5,6,7,8),each=10) #addinf the "other" column for each person participants play against

#Creating the column "other"
df_long <- df_long %>% 
  group_by(ParticipantCode) %>% 
  mutate(Other = x)

pacman::p_load(tidyverse, ggpubr, groupdata2, lme4, lmerTest)

df_long["Response"]<- df_respons_long$Response #lagging response and offer
df_long <- df_long %>% 
  group_by(ParticipantCode, Other) %>% 
  mutate(PrevOffer = lag(Offer),
         PrevResponse =lag(Response))

#adding centered previous offer
df_long <- df_long %>% 
  group_by(ParticipantCode, Other) %>% 
  mutate(centered_PrevOffer = ( PrevOffer - 50))

#setting variables as factors
df_long$Gender<-as.factor(df_long$Gender)
df_long$ParticipantCode<-as.factor(df_long$ParticipantCode)
```



#--------ANALYSIS-------

-
-
#plots before analysis
```{r}
library()
#checking data, effect for gender and is anonymous
ggplot(df_long, aes(Offer, color = Gender)) + 
  geom_density() + 
  facet_wrap(~Other) + 
  theme_minimal()

#log transforming offer to check if it gets better, it does not

df_long["log_offer"]<-log(df_long$Offer)

non_log<-ggplot(df_long, aes(Offer)) + 
  geom_density() + 
  scale_color_colorblind()+
  theme_minimal()

log<-ggplot(df_long, aes(log_offer)) + 
  geom_density() + 
  scale_color_colorblind()+
  theme_minimal()

log+non_log #comparing plots

#checking for ratio between accept or decline between personas
ggplot(df_long, aes(Response)) + 
  stat_count()+
  facet_wrap(~Other) + 
  theme_minimal()

```





-

#stats on mean age and gender
```{r}
#Age:
mean(df_long$Age) #26.57
sd(df_long$Age) #10.29

#Gender:
sum(df_wide$Consentform.1.player.Gender == 1)
#men: 26-11 = 15

box<-boxplot(df_long$Offer,
  ylab = "Offer"
)

#Creating botxplot to check outliers
plot1<-ggplot(df_long,aes(Offer, color="dose"))+
geom_boxplot(outlier.colour="black", outlier.shape=16, outlier.size=2, notch=FALSE)+theme(panel.background = element_blank())

plot1

```

-
#Percent of decline
```{r}
Percent_decline<-sum(df_long$Response == "Decline")/(sum(df_long$Response == "Accept")+sum(df_long$Response == "Decline"))*100
#calculating the decline percent across all participants and rounds
Percent_decline
```

Gender prior information from: https://onlinelibrary.wiley.com/doi/pdf/10.1111/j.1465-7295.2001.tb00060.x?casa_token=C1nTDoIOaz0AAAAA:TZGS37O8UK8c1PgbNEeVOIcRPL55kz0H_N1nuEwNiFlgWVMelV3S-_IWEIXKeaRNthK7Kz9g6fXf_A  

Models I have made for hyp 1:
bf(Offer ~ 1 + Is_anonymous + Gender + (1 |ParticipantCode)) 

bf(Offer ~ 1 + Is_anonymous + Gender + PrevResponse + (1 |ParticipantCode))

bf(Offer ~ 1 + Is_anonymous + Gender + PrevResponse + PrevResponse:centered_PrevOffer + (1 | ParticipantCode))

For Hyp 2:

Offer_semantic<- bf(Offer ~ 1 + Semantic_distance + Gender + PrevResponse + (1 |ParticipantCode)) 


-
#1. Predicting Offer based on anonymous condition, gender with random intercept of ParticipantCode (students t and gaussian)

bf(Offer ~ 1 + Is_anonymous + Gender + (1 |ParticipantCode))

#model1
```{r}

pacman::p_load("readr", "rethinking", "brms", "tidyverse", "patchwork", "metafor", ggthemes)

m1_OfferFormula<- bf(Offer ~ 1 + Is_anonymous + Gender + (1 |ParticipantCode)) #defining first formula, by nesting #Is_anonymous with participants I allow the same participant to start "new" with the conditions

get_prior(m1_OfferFormula, data = df_long, family = gaussian) 

mean(df_long$Offer) #checking the mean of offers and the sd
sd(df_long$Offer)


data_prior_m1_OfferFormula <- c(
  prior(normal(45,4), class = Intercept), #from the mean of all offers which is 40. I set 10 as sd so it can vary between 20 and 70
  prior(normal(-2,1), class = b, coef = Gender2), #Assume Gender2 (male) offer a mean of 5 in difference with sd of 2.5 (can go from 0 to 10)
  prior(normal(0,2), class = b, coef = Is_anonymous1), #Assume no difference... let the data "convince" while allowing the effect to go to 4
  prior(normal(4,2), class = sd, group = ParticipantCode),
  prior(normal(12,2), class = sigma))

#Make first model with gaussian

M1_gaussian<-brm(
  m1_OfferFormula,
  data=df_long,
  family= gaussian(),
  prior=data_prior_m1_OfferFormula,
  sample_prior="only",
  chains = 2,
  cores = 2,
)

pp_m1_gaussian<-pp_check(M1_gaussian, nsamples = 100) #doing ppcheck
pp_m1_gaussian

#Make first model with students t:
#m1_student<-brm(
#  m1_OfferFormula,
#  data=df_long,
#  family= student(),
#  prior=data_prior_m1_OfferFormula,
#  sample_prior="only",
#  chains = 2,
#  cores = 2
#)

#choosing to go with gaussian distribution
#pp_m1_student<-pp_check(m1_student, nsamples = 100)
#pp_m1_student


#Training the model on data
#Model with sampling from data

M1_gaussian_post<-brm(
  m1_OfferFormula,
  data=df_long,
  family= gaussian(),
  prior=data_prior_m1_OfferFormula ,
  sample_prior=T,
  chains = 2,
  cores = 2,
)

summary(M1_gaussian_post) #getting summary output
posterior_M1_Gaussian <-  posterior_samples(M1_gaussian_post) #sampling from the posterior
```

-
-
#Plots
```{r}
## anonymous
m1_anonymous<- ggplot(posterior_M1_Gaussian) +
  theme_classic() +
  geom_density(aes(prior_b_Is_anonymous1), fill="red", alpha=0.3) +
  geom_density(aes(b_Is_anonymous1), fill="blue", alpha=0.5)


m1_ParticipantCode<- ggplot(posterior_M1_Gaussian) +
  theme_classic() +
  geom_density(aes(prior_sd_ParticipantCode), fill="red", alpha=0.3) +
  geom_density(aes(sd_ParticipantCode__Intercept), fill="blue", alpha=0.5)


m1_sigma<- ggplot(posterior_M1_Gaussian) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5)

m1_Intercept<- ggplot(posterior_M1_Gaussian) +
  theme_classic() +
  geom_density(aes(prior_Intercept), fill="red", alpha=0.3) +
  geom_density(aes(b_Intercept), fill="blue", alpha=0.5)

m1_ParticipantCode+m1_sigma+m1_Intercept

library("patchwork")

## gender
m1_Gender2<- ggplot(posterior_M1_Gaussian) +
  theme_classic() +
  geom_density(aes(prior_b_Gender2), fill="red", alpha=0.3) +
  geom_density(aes(b_Gender2), fill="blue", alpha=0.5)
m1_anonymous+m1_Gender2

```

-
#redoing model 1
```{r}

#new priors:
data_prior2_m1_OfferFormula <- c(
  prior(normal(45,4), class = Intercept), #from the mean of all offers which is 40. I set 10 as sd so it can vary between 20 and 70
  prior(normal(-2,4), class = b, coef = Gender2), #Assume Gender2 (male) offer a mean of 5 in difference with sd of 2.5 (can go from 0 to 10)
  prior(normal(0,6), class = b, coef = Is_anonymous1), #Assume no difference... let the data "convince" while allowing the effect to go to 4
  prior(normal(8,3), class = sd, group = ParticipantCode),
  prior(normal(12,2), class = sigma))


#run model again:
M1_gaussian2<-brm(
  m1_OfferFormula,
  data=df_long,
  family= gaussian(),
  prior=data_prior2_m1_OfferFormula,
  sample_prior="only",
  chains = 2,
  cores = 2,
)
pp_m1_gaussian2<-pp_check(M1_gaussian2, nsamples = 100)
pp_m1_gaussian2

#Make model when sampling from data with 4 chains

M1_gaussian2_post<-brm(
  m1_OfferFormula,
  data=df_long,
  family= gaussian(),
  prior=data_prior2_m1_OfferFormula,
  sample_prior=T,
  chains = 4,
  cores = 2,
)


posterior_M1_Gaussian2 <-  posterior_samples(M1_gaussian2_post) #sampling from the posterior
summary(M1_gaussian2_post) #getting summary output

```

-
#checking chains
```{r}
pacman::p_load(bayesplot,viridis,mice)

color_scheme_set("viridis")
mcmc_rank_overlay(M1_gaussian2_post, pars = "b_Intercept", "b_Gender2") + theme_classic()

mcmc_rank_overlay(M1_gaussian2_post, pars = "b_Intercept", "b_Is_anonymous1") + theme_classic()
```

-
#plots2
```{r}
m1.2_Is_anonymous1<- ggplot(posterior_M1_Gaussian2) +
  theme_classic() +
  geom_density(aes(prior_b_Is_anonymous1), fill="red", alpha=0.3) +
  geom_density(aes(b_Is_anonymous1), fill="blue", alpha=0.5)


## gender
m1.2_Gender2<- ggplot(posterior_M1_Gaussian2) +
  theme_classic() +
  geom_density(aes(prior_b_Gender2), fill="red", alpha=0.3) +
  geom_density(aes(b_Gender2), fill="blue", alpha=0.5)


m1.2_Gender2+m1.2_Is_anonymous1

## anonymous
m1.2_Is_anonymous1<- ggplot(posterior_M1_Gaussian2) +
  theme_classic() +
  geom_density(aes(prior_b_Is_anonymous1), fill="red", alpha=0.3) +
  geom_density(aes(b_Is_anonymous1), fill="blue", alpha=0.5)


m1.2_ParticipantCode<- ggplot(posterior_M1_Gaussian2) +
  theme_classic() +
  geom_density(aes(prior_sd_ParticipantCode), fill="red", alpha=0.3) +
  geom_density(aes(sd_ParticipantCode__Intercept), fill="blue", alpha=0.5)

m1.2_sigma<- ggplot(posterior_M1_Gaussian2) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5)

m1.2_Intercept<- ggplot(posterior_M1_Gaussian2) +
  theme_classic() +
  geom_density(aes(prior_Intercept), fill="red", alpha=0.3) +
  geom_density(aes(b_Intercept), fill="blue", alpha=0.5)


m1.2_ParticipantCode+m1.2_sigma+m1.2_Intercept
```


-
#conditional effects plot for M1_gaussian
```{r}

plot(conditional_effects(M1_gaussian2_post, spaghetti=T, nsamples=100, method = "fitted"), points=T)

plot(conditional_effects(M1_gaussian2_post, spaghetti=T, nsamples=100, method = "predict"), points=T)

```




--

#2. Predicting Offer based on anoynomus condition, gender, PrevResponse + random intercept for participantCode

 bf(Offer ~ 1 + Is_anonymous + Gender + PrevResponse + (1 |ParticipantCode))
 
#Mdodel2
```{r}
m1_PrevResponse<- bf(Offer ~ 1 + Is_anonymous + Gender + PrevResponse + (1 |ParticipantCode))

get_prior(m1_PrevResponse, data = df_long, family = gaussian) 

#setting priors
data_prior_m1_PrevResponse <- c(
  prior(normal(45,4), class = Intercept), 
  prior(normal(-2,4), class = b, coef = Gender2),
  prior(normal(0,6), class = b, coef = Is_anonymous1),
  prior(normal(0,4), class = b, coef = PrevResponseDecline),
  prior(normal(8,3), class = sd),
  prior(normal(12,2), class = sigma))



#Make first model

M2_PrevResponse<-brm(
  m1_PrevResponse,
  data=df_long,
  family= gaussian(),
  prior=data_prior_m1_PrevResponse,
  sample_prior="only",
  chains = 2,
  cores = 2,
)

pp_m2_PrevResponse<-pp_check(M2_PrevResponse, nsamples = 100)
pp_m2_PrevResponse

#Make first model, train on data with 4 chains
M2_PrevResponse_post<-brm(
  m1_PrevResponse,
  data=df_long,
  family= gaussian(),
  prior=data_prior_m1_PrevResponse,
  sample_prior=T,
  chains = 4,
  cores = 2,
)


posterior_M2_PrevResponse <-  posterior_samples(M2_PrevResponse_post) #sampling from posterior
warnings() #checking warnings

summary(M2_PrevResponse_post)



```


-
#Chains trace check
```{r}
mcmc_rank_overlay(M2_PrevResponse_post, pars = "b_Intercept", "b_rPevResponseDecline") + theme_classic()

mcmc_rank_overlay(M2_PrevResponse_post, pars = "b_Intercept", "b_Is_anonymous1") + theme_classic()
```


-
#plots m2
```{r}
##prevresponseDecline
m2_PrevResponseDecline<- ggplot(posterior_M2_PrevResponse) +
  theme_classic() +
  geom_density(aes(prior_b_PrevResponseDecline), fill="red", alpha=0.3) +
  geom_density(aes(b_PrevResponseDecline), fill="blue", alpha=0.5)


## anonymous
m2_Is_anonymous1<- ggplot(posterior_M2_PrevResponse) +
  theme_classic() +
  geom_density(aes(prior_b_Is_anonymous1), fill="red", alpha=0.3) +
  geom_density(aes(b_Is_anonymous1), fill="blue", alpha=0.5)


## gender
m2_Gender2<- ggplot(posterior_M2_PrevResponse) +
  theme_classic() +
  geom_density(aes(prior_b_Gender2), fill="red", alpha=0.3) +
  geom_density(aes(b_Gender2), fill="blue", alpha=0.5)


m2_PrevResponseDecline+m2_Is_anonymous1+m2_Gender2

#Participantcode
m2_ParticipantCode<- ggplot(posterior_M2_PrevResponse) +
  theme_classic() +
  geom_density(aes(prior_sd_ParticipantCode), fill="red", alpha=0.3) +
  geom_density(aes(sd_ParticipantCode__Intercept), fill="blue", alpha=0.5)

#sigma
m2_sigma<- ggplot(posterior_M2_PrevResponse) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5)
p3

#intercept
m2_Intercept<- ggplot(posterior_M2_PrevResponse) +
  theme_classic() +
  geom_density(aes(prior_Intercept), fill="red", alpha=0.3) +
  geom_density(aes(b_Intercept), fill="blue", alpha=0.5)


m2_Intercept+m2_sigma+m2_ParticipantCode

```



-
#conditional effects
```{r}
plot(conditional_effects(M2_PrevResponse_post, spaghetti=T, nsamples=100, method = "fitted"), points=T)

plot(conditional_effects(M2_PrevResponse_post, spaghetti=T, nsamples=100, method = "predict"), points=T)

```






#3. Predicting Offer based on anoynomus condition, gender, PrevResponse + prevResponse:PrevOffer

bf(Offer ~ 1 + Is_anonymous + Gender + PrevResponse + PrevResponse:centered_PrevOffer + (1 | ParticipantCode))

#Model
```{r}

M3_interaction<- bf(Offer ~ 1 + Is_anonymous + Gender + PrevResponse + PrevResponse:centered_PrevOffer + (1 | ParticipantCode))

get_prior(M3_interaction, data = df_long, family = gaussian) 


#setting priors
data_prior_M3_interaction <- c(
  prior(normal(45,4), class = Intercept), 
  prior(normal(-2,8), class = b, coef = Gender2),
  prior(normal(0,6), class = b, coef = Is_anonymous1),
  prior(normal(0,4), class = b, coef = PrevResponseDecline),
  prior(normal(0,0.5), class = b, coef = PrevResponseAccept:centered_PrevOffer),#setting sceptical prior
  prior(normal(0,0.5), class = b, coef = PrevResponseDecline:centered_PrevOffer), #setting sceptical prior
  prior(normal(8,3), class = sd),
  prior(normal(8,2), class = sigma))

#Make first model
M3_interaction<-brm(
  M3_interaction,
  data=df_long,
  family= gaussian(),
  prior=data_prior_M3_interaction,
  sample_prior="only",
  chains = 4,
  cores = 2,
)


pp_M3_interaction<-pp_check(M3_interaction, nsamples = 100)
pp_M3_interaction

df_long$PrevResponse<-as.factor(df_long$PrevResponse)

#train model on data
M3_interaction_post<-brm(
  M3_interaction,
  data=df_long,
  family= gaussian(),
  prior=data_prior_M3_interaction,
  sample_prior=T,
  chains = 4,
  cores = 2,
)
posterior_M1_interaction <-  posterior_samples(M3_interaction_post)


summary(M3_interaction_post)

```

-
#checking chain trace 
```{r}
mcmc_rank_overlay(M3_interaction_post, pars = "b_Intercept", "b_Is_anonymous1") + theme_classic()

mcmc_rank_overlay(M3_interaction_post, pars = "b_Intercept","b_Gender2") + theme_classic()

mcmc_rank_overlay(M3_interaction_post, pars = "b_PrevResponseDecline", "PrevResponseDecline:centered_PrevOffer") + theme_classic()

mcmc_rank_overlay(M3_interaction_post, pars = "b_PrevResponseDecline", "PrevResponseAccept:centered_PrevOffer") + theme_classic()
```


-
#Plots model 3
```{r}

colnames(posterior_M1_interaction) <- sub(":", "", colnames(posterior_M1_interaction))

p3.M1_Interaction<- ggplot(posterior_M1_interaction) +
  theme_classic() +
  geom_density(aes(prior_b_PrevResponseDeclinecentered_PrevOffer), fill="red", alpha=0.3) +
  geom_density(aes(b_PrevResponseDeclinecentered_PrevOffer), fill="blue", alpha=0.5)

p3.M1_Interaction

p1.2_prev_other6 <- ggplot(posterior_M1_interaction) +
  theme_classic() +
  geom_density(aes(prior_b_PrevResponseAcceptcentered_PrevOffer), fill="red", alpha=0.3) +
  geom_density(aes(b_PrevResponseAcceptcentered_PrevOffer), fill="blue", alpha=0.5)

p1.2_prev_other6 + p3.M1_Interaction

p1.2<- ggplot(posterior_M1_interaction) +
  theme_classic() +
  geom_density(aes(prior_b_Is_anonymous1), fill="red", alpha=0.3) +
  geom_density(aes(b_Is_anonymous1), fill="blue", alpha=0.5)
p1.2

library("patchwork")

## gender
p3.2<- ggplot(posterior_M1_interaction) +
  theme_classic() +
  geom_density(aes(prior_b_Gender2), fill="red", alpha=0.3) +
  geom_density(aes(b_Gender2), fill="blue", alpha=0.5)

p3.2

p1.2+p3.2

## anonymous
p1<- ggplot(posterior_M1_interaction) +
  theme_classic() +
  geom_density(aes(prior_b_Is_anonymous1), fill="red", alpha=0.3) +
  geom_density(aes(b_Is_anonymous1), fill="blue", alpha=0.5)
p1


p2<- ggplot(posterior_M1_interaction) +
  theme_classic() +
  geom_density(aes(prior_sd_ParticipantCode), fill="red", alpha=0.3) +
  geom_density(aes(sd_ParticipantCode__Intercept), fill="blue", alpha=0.5)
p2

p3<- ggplot(posterior_M1_interaction) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5)
p3

p4<- ggplot(posterior_M1_interaction) +
  theme_classic() +
  geom_density(aes(prior_Intercept), fill="red", alpha=0.3) +
  geom_density(aes(b_Intercept), fill="blue", alpha=0.5)
p4

p3+p4+p2



```



---(not use below)----

-
#Conditional effects plots
```{r}

plot(conditional_effects(M3_interaction_post, spaghetti=T,nsamples=100, method ="predict"), points=T)
plot(conditional_effects(M3_interaction_post, spaghetti=T,nsamples=100, method ="fitted"), points=T)
```



-
#loo compare
```{r}

loo_m2 <- add_criterion(M2_PrevResponse_post, criterion = "loo")

loo_m3 <- add_criterion(M3_interaction_post, criterion = "loo")

loo_model_weights(loo_m2, loo_m3)

loo_compare(loo_m2, loo_m3)

```



#2.2 Cosine similarity


#model 1
Offer_BigModel<- bf(Offer ~ 1 + Scaled_sem + Gender + PrevResponse + Other + (1 |ParticipantCode)) 
```{r}

new_dataset["Scaled_sem"]<-scale(new_dataset$Semantic_distance)

new_dataset$Gender<-as.factor(new_dataset$Gender)
Offer_BigModel<- bf(Offer ~ 1 + Scaled_sem + Gender + PrevResponse + (1 |ParticipantCode)) 

get_prior(Offer_BigModel, data = 
new_dataset, family = gaussian) 

mean(new_dataset$Offer)
sd(new_dataset$Offer)
#setting priors

Offer_BigModel_prior <- c(
  prior(normal(45,4), class = Intercept), 
  prior(normal(-2,8), class = b, coef = Gender2), 
  prior(normal(0,4), class = b, coef = PrevResponseDecline), 
  prior(normal(3,2), class = b, coef = Scaled_sem),
  prior(normal(12,3), class = sd),
  prior(normal(12,2), class = sigma))

#running model with prior 
Prior_Offer_BigModel<-brm(
  Offer_BigModel,
  data=new_dataset,
  family= gaussian(),
  prior=Offer_BigModel_prior,
  sample_prior="only",
  chains = 2,
  cores = 2,
)


pp_Offer_BigModel<-pp_check(Prior_Offer_BigModel, nsamples = 100)

pp_Offer_BigModel

#Training the model on data with 4 chains
Post_Offer_BigModel<-brm(
  Offer_BigModel,
  data=new_dataset,
  family= gaussian(),
  prior=Offer_BigModel_prior,
  sample_prior=T,
  chains = 4,
  cores = 2,
)

summary(Post_Offer_BigModel)
Post_Offer_BigModel_posterior<-  posterior_samples(Post_Offer_BigModel)
```
-
-
#checking chains
```{r}
mcmc_rank_overlay(Post_Offer_BigModel, pars = "b_Intercept", "b_Scaled_sem") + theme_classic()

mcmc_rank_overlay(Post_Offer_BigModel, pars = "b_Intercept","b_Gender2") + theme_classic()

mcmc_rank_overlay(Post_Offer_BigModel, pars = "b_Intercept","b_PrevResponseDecline") + theme_classic()

```

-
#plots
```{r}
p1_prevResponse<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_b_PrevResponseDecline), fill="red", alpha=0.3) +
  geom_density(aes(b_PrevResponseDecline), fill="blue", alpha=0.5)
p1_prevResponse

library("patchwork")

## gender
p2_prevResponse<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_b_Gender2), fill="red", alpha=0.3) +
  geom_density(aes(b_Gender2), fill="blue", alpha=0.5)

p2_prevResponse


p1_prevResponse+p2_prevResponse+p1.2

p1.2<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_b_Scaled_sem), fill="red", alpha=0.3) +
  geom_density(aes(b_Scaled_sem), fill="blue", alpha=0.5)
p1.2

library("patchwork")

## gender
p3.2<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_b_Gender2), fill="red", alpha=0.3) +
  geom_density(aes(b_Gender2), fill="blue", alpha=0.5)

p3.2

p1.2+p3.2+p1_prevResponse

## anonymous
p1<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_b_Is_anonymous1), fill="red", alpha=0.3) +
  geom_density(aes(b_Is_anonymous1), fill="blue", alpha=0.5)
p1


p2<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_sd_ParticipantCode), fill="red", alpha=0.3) +
  geom_density(aes(sd_ParticipantCode__Intercept), fill="blue", alpha=0.5)
p2

p3<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5)
p3

p4<- ggplot(Post_Offer_BigModel_posterior) +
  theme_classic() +
  geom_density(aes(prior_Intercept), fill="red", alpha=0.3) +
  geom_density(aes(b_Intercept), fill="blue", alpha=0.5)
p4

p3+p4+p2
```



#checking conditional effects
```{r}
plot(conditional_effects(Post_Offer_BigModel, spaghetti=T,nsamples=100, method ="predict"), points=T)
plot(conditional_effects(Post_Offer_BigModel, spaghetti=T,nsamples=100, method ="fitted"), points=T)
```




#---Persona Semantic Preprocessing-----

#Making Persona dataframes with one word in each row
```{r include=FALSE}
library(dplyr)
library(tidytext)


library(data.table)
#load("EN_100k_lsa.rda")
EN100k<-as.data.frame(EN_100k_lsa)

setDT(EN100k, keep.rownames = TRUE)[]

Persona_df <- data.frame (Descriptions = c('I am a 24 year old woman and I study international business communication in Spanish on 5th semester at bachelor’s level. In my spare time I’m active in a political youth party and I like going on long walks with my friends from my studies and the party. During corona I have been baking sourdough bread and started going for walks.','Work as a personal consultant in Danske bank guiding clients with investments. When I’m off work, I am together with my fiancé and kids. I golf and ride mountain bike with my coworkers in the weekends/off-work days','My name is Camilla and I’m 19 years old. Im in 3.G in Gymnasium and become a student in June. After the summer i want to study a bachelor in law at Aalborg university and move there with my two friends from my gymnasium. In my spare time i read a lot and watch some Netflix shows.','I am 23 years old and work part time in Bilka in the garden department. I like taking rides on my motorcycle. I enjoy gardening, cooking and spending time with my friends and play with my cat. I am trying to get a job as an environmental technologist. I am not doing much during these times, looking forward to an open world again so I can travel.','I’m 21 years old and a student.I study datascience and I have a student-job at a printer firm. In my free time I 
play piano, paint and read books. I also enjoy watching YouTube and I spend way too much time on Twitter'),
Persona=c("Persona_1","Persona_2","Persona_3","Persona_4","Persona_5"))

#running the first participant through the sentiment analysis in order to rowbind the following participants to the dataframe
text<-c(Persona_df$Descriptions[1]) 
persona_about_you_word<-data.frame(text) %>% unnest_tokens(word, text)

sentiment_persona<-filter(EN100k, rn %in% persona_about_you_word$word) %>% 
  mutate(Persona = Persona_df$Persona[1]) %>% 
  relocate(Persona, .before = rn)  %>% 
  rename(word = rn)

#loop through each participant and adding their sentiment scores
for (row_nr in 2:nrow(Persona_df)){
  
  text<-c(Persona_df$Descriptions[row_nr])
  
  about_you_word<-data.frame(text) %>% unnest_tokens(word, text)
  
  temporary_sentiment<-filter(EN100k, rn %in% about_you_word$word) %>% 
    
  mutate(Persona = Persona_df$Persona[row_nr]) %>% 
  relocate(Persona, .before = rn)  %>% 
  rename(word = rn)
  
  sentiment_persona<-rbind(sentiment_persona, temporary_sentiment)
}

sentiment_persona<-as.data.frame(sentiment_persona)  #setting it as dataframe
mean <- aggregate(sentiment_persona[,3:302], list(sentiment_persona$Persona), FUN = mean) #taking average of each semantic dimension across words for each participant

mean_persona<-mean %>% rename(Persona =Group.1)

```

-
#merging EN_100K with about you for participants
```{r}


class(df_wide$participant.code)

df_wide$participant.code<-as.factor(df_wide$participant.code)
about_youDf<-data.frame(about_youDf)

about_youDf["ParticipantCode"]<- df_wide$participant.code #adding participant code
View(about_youDf)

#running the first participant through the sentiment analysis in order to rowbind the following participants to the dataframe
text_participants<-c(about_youDf$about_youDf[1]) 
about_you_word<-data.frame(text) %>% unnest_tokens(word, text)

sentiment<-filter(EN100k, rn %in% about_you_word$word) %>% 
  mutate(PartcipantCode = about_youDf$ParticipantCode[1]) %>% 
  relocate(PartcipantCode, .before = rn)  %>% 
  rename(word = rn)

#loop through each participant and adding their sentiment scores
for (row_nr in 2:nrow(about_youDf)){
  
  text<-c(about_youDf$about_youDf[row_nr])
  
  about_you_word<-data.frame(text) %>% unnest_tokens(word, text)
  
  temporary_sentiment<-filter(EN100k, rn %in% about_you_word$word) %>% 
    
  mutate(PartcipantCode = about_youDf$ParticipantCode[row_nr]) %>% 
  relocate(PartcipantCode, .before = rn)  %>% 
  rename(word = rn)
  
  sentiment<-rbind(sentiment, temporary_sentiment)
}

sentiment<-as.data.frame(sentiment)  #setting it as dataframe
mean <- aggregate(sentiment[,3:302], list(sentiment$PartcipantCode), FUN = mean) #taking average of each semantic dimension across words for each participant

mean<-mean %>% rename(ParticipantCode =Group.1)

new_dataset<-read_csv("Cosine-similaritydf.csv")


```


```{r}
library(pacman)
#install.packages("SnowballC")
#install.packages("lsa")
library(lsa)

```
-
#persona1

```{r}
#Trying to calculate 1 semantic distance:

mean_persona_V<-mean_persona[,2:301]

mean_participant_V<-mean[,2:301]

vec1<-c(as.vector(mean_participant_V[1,1:300]))
vec1<- as.numeric(unlist(vec1))

vec2<-c(as.vector(mean_persona_V[1,1:300]))
vec2<- as.numeric(unlist(vec2))

cos_similarity<-cosine(vec1,vec2)
cos_similarity
cos_similarity<-as.data.frame(cos_similarity)

#for persona 1:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[1,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity<-rbind(cos_similarity, cos_sim)
}

cos_similarity["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```

-
#Persona2
```{r}
#Trying to calculate 1 semantic distance:

vec2<-c(as.vector(mean_participant_V[1,1:300]))
vec2<- as.numeric(unlist(vec2))

vec3<-c(as.vector(mean_persona_V[2,1:300]))
vec3<- as.numeric(unlist(vec3))

cos_similarity_Persona2<-cosine(vec2,vec3)

cos_similarity_Persona2<-as.data.frame(cos_similarity_Persona2)

#for persona 2:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[2,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity_Persona2<-rbind(cos_similarity_Persona2, cos_sim)
}

cos_similarity_Persona2["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```



-
#Persona3
```{r}
#Trying to calculate 1 semantic distance:

vec3<-c(as.vector(mean_participant_V[1,1:300]))
vec3<- as.numeric(unlist(vec3))

vec4<-c(as.vector(mean_persona_V[3,1:300]))
vec4<- as.numeric(unlist(vec4))

cos_similarity_Persona3<-cosine(vec3,vec4)

cos_similarity_Persona3<-as.data.frame(cos_similarity_Persona3)

#for persona 3:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[3,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity_Persona3<-rbind(cos_similarity_Persona3, cos_sim)
}

cos_similarity_Persona3["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```


-
#Persona4
```{r}
#Trying to calculate 1 semantic distance:

vec4<-c(as.vector(mean_participant_V[1,1:300]))
vec4<- as.numeric(unlist(vec4))

vec5<-c(as.vector(mean_persona_V[4,1:300]))
vec5<- as.numeric(unlist(vec5))

cos_similarity_Persona4<-cosine(vec4,vec5)

cos_similarity_Persona4<-as.data.frame(cos_similarity_Persona4)

#for persona 4:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[4,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity_Persona4<-rbind(cos_similarity_Persona4, cos_sim)
}

cos_similarity_Persona4["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```

-
#Persona5
```{r}
#Trying to calculate 1 semantic distance:

vec4<-c(as.vector(mean_participant_V[1,1:300]))
vec4<- as.numeric(unlist(vec4))

vec5<-c(as.vector(mean_persona_V[5,1:300]))
vec5<- as.numeric(unlist(vec5))

cos_similarity_Persona5<-cosine(vec4,vec5)

cos_similarity_Persona5<-as.data.frame(cos_similarity_Persona5)

#for persona 5:
for (row_nr in 2:nrow(mean_participant_V)){
  
  vec1<-c(as.vector(mean_participant_V[row_nr,1:300]))
  vec1<- as.numeric(unlist(vec1))
  
  vec2<-c(as.vector(mean_persona_V[5,1:300]))
  vec2<- as.numeric(unlist(vec2))

  cos_sim<-cosine(vec1,vec2)
  
  cos_similarity_Persona5<-rbind(cos_similarity_Persona5, cos_sim)
}

cos_similarity_Persona5["ParticipantCode"]<- df_wide$participant.code #binding participant to the df
```

-
#Merging all 5 dataframes together
```{r}

Cosine_similarity_df<-rbind(cos_similarity,cos_similarity_Persona2,cos_similarity_Persona3,cos_similarity_Persona4,cos_similarity_Persona5)

```


-
#Filtering The df_long to only contain non-anonymous condition:
```{r}
library(tidyverse)
library(dplyr)

filteredForNA<-filter(df_long, Is_anonymous == 0)
filteredForNA$Round<-as.factor(filteredForNA$Round)

x<-rep(c(4,5,6,7,8),each= 26)

Cosine_similarity_df <- Cosine_similarity_df %>% 
  mutate(Other = x)

new_dataset <- filteredForNA %>% right_join(Cosine_similarity_df, by=c("ParticipantCode","Other"))   %>% rename(
    Semantic_distance = V1
    )

  
#write.csv(new_dataset,"/Users/annahedvigmoller/Elgiganten Cloud/Uni/4. Semester/Social cultural #dynamics/sockult_exam_new/Aanlysis/Cosine-similaritydf.csv", row.names = TRUE)

```

